Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-07-19 paper/v1.0/sections/8_manipulate_conductivity.tex
Improve figures and results

To identify the characteristics of the transverse conductivity of the quantum Hall systems with external dressing field, first we can derive a expression for a normalized
transverse conductivity as a function of fermi energy $X_F$ and intensity of the dressing field $I$. Here we have normalized the conductivity using the natural conductivity of least Landau level.
\begin{equation} \label{eq_35}
  \begin{aligned}
    \sigma^{xx}(X_F,I) = &
    \sum_{n}
    \frac{\qty(n+1)}{0.0037\Lambda_n \Lambda_{n+1}} \\
    & \times
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n -1}{0.06\Lambda_n})^2
      }
    ]
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n}{0.06\Lambda_{n+1}})^2
      }
    ]
  \end{aligned}
\end{equation}
We use this expression to illustrate the changes that can be done to the transverse conductivity in 2DEG using external dressing field. As given in Fig.~\ref{fig_4} and \ref{fig_5} we can manipulate the transverse conductivity $\sigma_{xx}$ using external dressing field's intensity and the Fermi level $X_F$ of the considering system. For a given dressing field intesity, the transverse conductivity vary against the Fermi level of the system by creating sharp peaks at each Landau level energy values. Since electrons are restricted to have only Landau level energies, the conductivity gets very low values when the Fermi level is not align with any of the Landau level energy values. In contrast, on Landau levels conductivity can achieve very high values compared to other areas and as illustrates on Fig.~\ref{fig_4} the peak value of transverse conductivity on each Landau level gets increase with the Landau level number.

\begin{figure}[t]
\includegraphics[scale=0.55]{figures/fig_5}
\caption{\label{fig_5} Normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$. In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
\end{figure}
\begin{figure}[t]
\includegraphics[scale=0.55]{figures/fig_6}
\caption{\label{fig_6} $3$rd Landau level’s normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$. In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$}.
\end{figure}

>>>>

To identify the characteristics of the transverse conductivity of the quantum Hall systems with external dressing field, first we can derive a expression for a normalized
transverse conductivity as a function of fermi energy $X_F$ and intensity of the dressing field $I$. Here we have the normalized x-directional conductivity using the natural conductivity of least Landau level
\begin{equation} \label{eq_35}
  \begin{aligned}
    \sigma^{xx}/\sigma^{0} = &
    \sum_{n}
    \frac{\qty(n+1)}{0.0037\Lambda_n \Lambda_{n+1}} \\
    & \times
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n -1}{0.06\Lambda_n})^2
      }
    ]
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n}{0.06\Lambda_{n+1}})^2
      }
    ]
  \end{aligned}
\end{equation}
where $\sigma^0 = (e^2/\pi \hbar A)$. We use this expression to illustrate the changes that can be done to the transverse conductivity in 2DEG using external dressing field. As given in Fig.~\ref{fig_4} and \ref{fig_5} we can manipulate the transverse conductivity $\sigma_{xx}$ using external dressing field's intensity and the Fermi level $X_F$ of the considering system. For a given dressing field intesity, the transverse conductivity vary against the Fermi level of the system by creating sharp peaks at each Landau level energy values. Since electrons are restricted to have only Landau level energies, the conductivity gets very low values when the Fermi level is not align with any of the Landau level energy values. In contrast, on Landau levels conductivity can achieve very high values compared to other areas and as illustrates on Fig.~\ref{fig_4} the peak value of transverse conductivity on each Landau level gets increase with the Landau level number.

\begin{figure}[t]
\includegraphics[scale=0.55]{figures/fig_5}
\caption{\label{fig_5} Normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$. In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
\end{figure}
\begin{figure}[t]
\includegraphics[scale=0.55]{figures/fig_6}
\caption{\label{fig_6} $3$rd Landau level’s normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$. In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$}.
\end{figure}
